Ab Initio Effective One-Electron Potentials Revisited: General Theory and Example Applications for Charge-Transfer Energy Calculations

### 2019-11-11 papers/2_oep_technique/paper-r1.tex
Removing derivation errors in the group II and III of OL and OEP-OL expressions

After the OEP technique has been formulated, it can be applied 
to the calculation of interaction\hyp{}induced properties following the
fragment\hyp{}based philosophy. 
According to the second\hyp{}order intermolecular perturbation theory of Murrell et al.,
the energy associated with the charge transfer from molecule $A$ to $B$ is given by
%
\begin{equation} \label{e:ct-murell-etal.e}
 E^{A\rightarrow B} = 2 \sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir} 
  \frac{\vert V^{A\rightarrow B}_{in} \vert^2 }{\varepsilon_i - \varepsilon_n}
\end{equation}
%
%coupling constants between occupied and virtual molecular orbitals 
%are re-expressed by the effective one-electron potentials. The resulting formula provides new possibilities 
%of optimization and applications in condensed phase simulations. [3]
%
where $\varepsilon_i$ and $\varepsilon_n$ are the canonical energies
of the occupied (denoted by `Occ') and virtual (denoted by `Vir') 
HF molecular orbitals, respectively,
whereas the coupling constant is given by
%
\begin{multline} \label{e:ct-murell-etal.vin}
 V^{A\rightarrow B}_{in} = 
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} \\
      - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik} \;.
\end{multline}
%
In the above expression, the following effective one\hyp{}electron operators,
%
\begin{subequations} 
\begin{align} \label{e:ct-murell-etal.vtot-vi}
 \hat{v}^B_{\rm tot} &= \hat{v}^B_{\rm nuc} + 2\sum_{j\in B}^{\rm Occ} \hat{v}^B_{jj} \quad\text{ and }\\ 
 \hat{v}^A_{i      } &= \hat{v}^A_{\rm tot} - 2\hat{v}^A_{ii} \;,
\end{align}
\end{subequations}
%
were introduced without making any approximation to the original equation
from Ref. 
The goal of this work is to apply the technique sketched in Eq.XXX
to eliminate ERI's from Eq.~\eqref{e:ct-murell-etal.vin} in terms of OEP's.

@@

\paragraph{Group (ii).}
The term belonging to this group can be considered as a sum of interaction
energies between the total charge density distribution of molecule $B$
and the partial density $\rho_{ik}({\bf r})$ of molecule $A$,
weighted by the overlap integrals $S_{nk}$. Using the distributed multipole 
expansion this group can be written as
%
\begin{equation} \label{e:ct.group-2}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \cong - \sum_{k\in A}^{\rm Occ} S_{nk} \rho_{ki}^A \odot \rho^B_{\rm tot} \;.
\end{equation}
%
Consider now a situation in which the localized occupied MO's are used.
If the multipole series expansions are truncated
at the distributed charges $q_i$ and dipole moments ${\BM{\upmu}_i}$, 
located at the centroids ${\bf r}_i = \tBraKet{i}{\hat{\bf r}}{i}$, 
then the interaction energy becomes
%
\begin{multline}
 \rho_{ki}^A \odot \rho^B_{\rm tot} 
 \approx 
 q_{ki} 
 \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{\vert {\bf r}_y - {\bf r}_i \vert } 
 +
 2\sum_{j\in B}^{\rm LC}
  \frac{q_j}{\vert {\bf r}_j - {\bf r}_i \vert } 
 \right] \\
 + \text{ dipole terms } \;.
\end{multline}
%
Note however that $q_{ik} = -\delta_{ik}$ and $q_j = -1$. Moreover, 
if the localized orbitals are perfectly spherical distributed dipole moments vanish.
This means that Eq.~\eqref{e:ct.group-2} can be approximated as follows:
%
\begin{equation} \label{e:ct.group-ii.final}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \approx S_{ni}  \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
 \right] \;.
\end{equation}
%
Therefore, only overlap integrals and relative distances between
atomic and LC's are needed, which leads to a great reduction of the
calculation cost,
as compared either to the original expression or to the multipole expansion (left\hyp{} and right\hyp{}hand sides
of Eq.~\eqref{e:ct.group-2}, respectively).
We shall refer to this approximation as to
the spherical overlap approximation (SOA). Note that in order for this approximation to be valid,
occupied molecular orbitals need to be localized.

\paragraph{Group (iii).}
The terms with the overlap integrals involving the occupied MO on $A$
can be combined into a single summation term, i.e.,
\begin{multline}
       - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik} \\ = -
 \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \tBraKet{j}{
 \underbrace{
 \left\{ 
  \delta_{ik} \left( \hat{v}^A_{k} + \hat{v}^A_{ik} \right)
  - \hat{v}^A_{ik}
 \right\} 
  }_{\hat{v}^{A,{\rm eff}}_{ik}}
 }{n}  \\ \cong -
%
  \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \rho_{nj}^B \odot \rho^{A,{\rm eff}}_{ik} \;,
\end{multline}
%
where the effective potential ${v}^{A,{\rm eff}}_{ik}$ (with the associated 
effective density $\rho^{A,{\rm eff}}_{ik}$) 
is defined by
%
\begin{equation} \label{e:ct.group-iii.oep}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \equiv
 \delta_{ik} 
 \left[
  v^A_{\rm tot} ({\bf r}) - 2 v^A_{kk} ({\bf r}) + v^A_{ik} ({\bf r})
 \right] 
  - v^A_{ik} ({\bf r}) \;.
\end{equation}
%
Now, it is first assumed here that $\rho^{B}_{nj} ({\bf r}) \approx 0$ if occupied MO's on $B$ are localized.
This means that
%
\begin{multline} \label{e:ct.group-iii.final.a}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik}  \\
 \approx 0 \;.
\end{multline}
%
The above result is a crude approximation, since the channels $j\rightarrow n$
are quite important contributions in most of perturbation theory treatments.
%virtual MO's can penetrate the occupied MO's to some extent.
In order to include the $\rho^{B}_{nj}$ density, it is approximately represented here by a set of effective 
cumulative
atomic charges $\{ q^{B,(nj)}_{y} \}$ associated with the effective one\hyp{}particle density matrix
%
\begin{equation}
 D^{B,(nj)}_{\beta\delta} = C_{\beta n} C_{\delta j} \;.
\end{equation}
%
In this work, the effective charges were computed via the CAMM or ESP methods as
discussed in Section~XXX. Applying the SOA 
and the effective potential from Eq.~\eqref{e:ct.group-iii.oep} 
leads to 
%
\begin{multline} \label{e:ct.group-iii.final.b}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{i} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \left( 1 - \delta_{ik} \right) 
        \BraKet{nj}{ik}  \\
 \approx  -
 \sum_{j\in B}^{\rm Occ} S_{ij}
 \sum_{y\in B}^{\rm At} 
 q^{B,(nj)}_{y} 
 \left[ 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
 \right]
 \;.
\end{multline}
%

\paragraph{Final OEP-based forms of the coupling constant.}
Gathering the results from Eqs. the coupling constant
can be given as follows
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep}
\Approx{ V_{in}^{A\rightarrow B} }{1}
       &= \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} 
 +
S_{ni} u_i^{BA} \;, \\
%
\Approx{ V_{in}^{A\rightarrow B} }{2} &=
\Approx{ V_{in}^{A\rightarrow B} }{1} -
  \sum_{j   \in B}^{\rm Occ} S_{ij}
  \sum_{y   \in B}^{\rm At} q_y^{B,(nj)} w_{yi}^{BA}
\;,
\end{align}
\end{subequations}
%
where the auxiliary variables are
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep.aux-var}
 u_i^{BA} &\equiv    
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
                \;, \\
 w_{yi}^{BA} &\equiv 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{2}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
                \;.
\end{align}
\end{subequations}
%
To compute the interaction energy due to CT from $A$ to $B$ by using the above SOA\hyp{}based
approximations, coupling elements need to be transformed from localized to canonical MO basis, i.e.,
%
\begin{equation} \label{e:ect-oep.prefinal}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{
 \lvert
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \Approx{V_{i'n}^{A\rightarrow B}}{} 
 \rvert^2 }{\varepsilon_i - \varepsilon_n} \;,
\end{equation}
%
where ${\bf L}^A$ is the CMO\hyp{}LMO transformation matrix for occupied orbitals of $A$. 
Note however, that the effective potential parameters from the density fitted term of group (i) 
do not involve any occupied orbitals.
Therefore, to save computational costs, only groups (ii) and (iii) need to be transformed
whereas for group (i) the overlap integrals from Eq.~\eqref{e:ct.group-i.final} 
can be already evaluated in CMO basis.
Thus, the final working formula for the interaction energy due to CT from $A$ to $B$ reads
%
\begin{multline} \label{e:ect-oep.final}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{1}{\varepsilon_i - \varepsilon_n} \times 
 \Bigg(
   \Approx{V_{in}^{A\rightarrow B}}{\rm G1} \\
  +
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \left\{
   \Approx{V_{i'n}^{A\rightarrow B}}{\rm G2} 
  +\Approx{V_{i'n}^{A\rightarrow B}}{\rm G3}
  \right\}
 \Bigg)^2 \;,
\end{multline}
%
where the subscripts G$n$ ($n$ = 1, 2, 3) denote a particular group of 
terms from Eqs.~\eqref{e:ct.group-i.final}, \eqref{e:ct.group-ii.final} and \eqref{e:ct.group-iii.final.a}
or \eqref{e:ct.group-iii.final.b}. 
The total CT energy is given by the sum of the above contribution and the twin contribution
due to CT from molecule $B$ to $A$.

>>>>

After the OEP technique has been formulated, it can be applied 
to the calculation of interaction\hyp{}induced properties following the
fragment\hyp{}based philosophy. 
According to the second\hyp{}order intermolecular perturbation theory of Murrell et al.,
the energy associated with the charge transfer from molecule $A$ to $B$ is given by
%
\begin{equation} \label{e:ct-murell-etal.e}
 E^{A\rightarrow B} = 2 \sum_{i\in A}^{\rm Occ} \sum_{n\in B}^{\rm Vir} 
  \frac{\vert V^{A\rightarrow B}_{in} \vert^2 }{\varepsilon_i - \varepsilon_n}
\end{equation}
%
%coupling constants between occupied and virtual molecular orbitals 
%are re-expressed by the effective one-electron potentials. The resulting formula provides new possibilities 
%of optimization and applications in condensed phase simulations. [3]
%
where $\varepsilon_i$ and $\varepsilon_n$ are the canonical energies
of the occupied (denoted by `Occ') and virtual (denoted by `Vir') 
HF molecular orbitals, respectively,
whereas the coupling constant is given by
%
\begin{multline} \label{e:ct-murell-etal.vin}
 V^{A\rightarrow B}_{in} = 
        \tBraKet{i}{\hat{v}^B_{\rm tot} }{n} 
      - \sum_{j\in B}^{\rm Occ} \BraKet{nj}{ij} 
      - \sum_{k\in A}^{\rm Occ} S_{nk} \left(1+\delta_{ik}\right) \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} \\
      - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} \BraKet{nj}{ik} \;.
\end{multline}
%
In the above expression, the following effective one\hyp{}electron operators,
%
\begin{subequations} 
\begin{align} \label{e:ct-murell-etal.vtot-vi}
 \hat{v}^B_{\rm tot} &= \hat{v}^B_{\rm nuc} + 2\sum_{j\in B}^{\rm Occ} \hat{v}^B_{jj} \quad\text{ and }\\ 
%\hat{v}^A_{i      } &= \hat{v}^A_{\rm tot} - 2\hat{v}^A_{ii} \;,
\end{align}
\end{subequations}
%
were introduced without making any approximation to the original equation
from Ref. 
The goal of this work is to apply the technique sketched in Eq.XXX
to eliminate ERI's from Eq.~\eqref{e:ct-murell-etal.vin} in terms of OEP's.

@@

\paragraph{Group (ii).}
The term belonging to this group can be considered as a sum of interaction
energies between the total charge density distribution of molecule $B$
and the partial density $\rho_{ik}({\bf r})$ of molecule $A$,
weighted by the overlap integrals $S_{nk}$. Using the distributed multipole 
expansion based on the charge centroids of the localized molecular orbitals (LMO's),
${\bf r}_i = \tBraKet{i}{\hat{\bf r}}{i}$ with $\chi_i({\bf r})$ being localized,
this group can be written as
%
\begin{equation} \label{e:ct.group-2}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \left(1+\delta_{ik}\right) \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \cong - \sum_{k\in A}^{\rm Occ} S_{nk} \left(1+\delta_{ik}\right) \rho_{ki}^A \odot \rho^B_{\rm tot} \;.
\end{equation}
%
Note that, in general, $\rho_{ki}^A$ is complex whereas $\rho^B_{\rm tot}$ is always real.
Since the interaction energy must also be real, it must hold that
%
\begin{equation} \label{e:ct.group-2-d}
 \rho_{ki}^A \odot \rho^B_{\rm tot} = \delta_{ik} \rho_{ii}^A \odot \rho^B_{\rm tot} \;.
\end{equation}
%
Consider now a situation in which the localized occupied MO's are used.
In this case, the distributed multipole expansion
of the above becomes
%
\begin{multline}
 \rho_{ii}^A \odot \rho^B_{\rm tot} 
 \approx 
 q_{i} 
 \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{\vert {\bf r}_y - {\bf r}_i \vert } 
 +
 2\sum_{j\in B}^{\rm LC}
  \frac{q_j}{\vert {\bf r}_j - {\bf r}_i \vert } 
 \right] \\
 + \text{ quadrupole terms } \;,
\end{multline}
%
because the distributed charges
$q_i = -1$ whereas the distributed dipole moments %${\BM{\upmu}_i}$ 
centered at their
respective LMO charge centroids vanish.
This means that Eq.~\eqref{e:ct.group-2} can be approximated as follows:
%
\begin{equation} \label{e:ct.group-ii.final}
      - \sum_{k\in A}^{\rm Occ} S_{nk} \left(1+\delta_{ik}\right) \tBraKet{k}{\hat{v}^B_{\rm tot} }{i} 
 \approx 2S_{ni}  \left[
  %\sum_{i\in A}^{\rm LC} 
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
 \right] \;.
\end{equation}
%
Therefore, only overlap integrals and relative distances between
atomic and LC's are needed, which leads to a great reduction of the
calculation cost,
as compared either to the original expression or to the multipole expansion (left\hyp{} and right\hyp{}hand sides
of Eq.~\eqref{e:ct.group-2}, respectively).
We shall refer to this approximation as to
the spherical overlap approximation (SOA). Note that in order for this approximation to be valid,
occupied molecular orbitals need to be localized.

\paragraph{Group (iii).}
The terms with the overlap integrals involving the occupied MO on $A$
can be combined into a single summation term, i.e.,
\begin{multline}
       - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} 
        \BraKet{nj}{ik} \\ = -
 \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \tBraKet{j}{
 \underbrace{
 \left\{ 
  \delta_{ik} \hat{v}^A_{\rm tot} - \hat{v}^A_{ik}
 \right\} 
  }_{\hat{v}^{A,{\rm eff}}_{ik}}
 }{n}  \\ \cong -
%
  \sum_{k\in A}^{\rm Occ} 
 \sum_{j\in B}^{\rm Occ}
 S_{kj} 
 \rho_{nj}^B \odot \rho^{A,{\rm eff}}_{ik} \;,
\end{multline}
%
where the effective potential ${v}^{A,{\rm eff}}_{ik}$ (with the associated 
effective density $\rho^{A,{\rm eff}}_{ik}$) 
is defined by
%
\begin{equation} \label{e:ct.group-iii.oep}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \equiv
 \delta_{ik} 
 {v}^A_{\rm tot} ({\bf r})- {v}^A_{ik} ({\bf r}) \;.
\end{equation}
%
Now, it is first assumed here that $\rho^{B}_{nj} ({\bf r}) \approx 0$ if occupied MO's on $B$ are localized.
This means that
%
\begin{equation} \label{e:ct.group-iii.final.a}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj} 
        \BraKet{nj}{ik} \approx 0 \;.
\end{equation}
%
The above result is a crude approximation, since the channels $j\rightarrow n$
are quite important contributions in most of perturbation theory treatments.
%virtual MO's can penetrate the occupied MO's to some extent.
In order to include the $\rho^{B}_{nj}$ density, it is approximately represented here by a set of effective 
cumulative
atomic charges $\{ q^{B,(nj)}_{y} \}$ associated with the effective one\hyp{}particle density matrix
%
\begin{equation}
 D^{B,(nj)}_{\beta\delta} = C_{\beta n} C_{\delta j} \;.
\end{equation}
%
In this work, the effective charges were computed via the CAMM or ESP methods as
discussed in Section~XXX. 
Note now that both effective densities in 
$\rho^B_{jn} \odot \rho^{A,{\rm eff}}_{ik}$ are generally complex and one cannot apply the SOA
for $\rho^{A,{\rm eff}}_{ik}$. In the LMO picture however, it can be shown that
$\rho_{ik} ({\bf r}) \ll \rho_{ii} ({\bf r})$ 
for $i\ne k$ in most locations. Therefore,
the SOA is still applicable in the LMO picture
and the effective potential from Eq.~\eqref{e:ct.group-iii.oep} 
simplifies to
%
\begin{equation} \label{e:ct.group-iii.oep.simplified}
 {v}^{A,{\rm eff}}_{ik}({\bf r}) \approx
 \delta_{ik} \left\{
 {v}^A_{\rm tot} ({\bf r})- {v}^A_{ii} ({\bf r}) \right\} \;,
\end{equation}
%
which
leads to 
%
\begin{multline} \label{e:ct.group-iii.final.b}
        - \sum_{j\in B}^{\rm Occ} S_{ij} \tBraKet{j}{\hat{v}^A_{\rm tot} }{n}  
     + \sum_{k\in A}^{\rm Occ} \sum_{j\in B}^{\rm Occ}  
        S_{kj}
        \BraKet{nj}{ik}  \\
 \approx  -
 \sum_{j\in B}^{\rm Occ} S_{ij}
 \sum_{y\in B}^{\rm At} 
 q^{B,(nj)}_{y} 
 \left[ 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{1}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
 \right]
 \;.
\end{multline}
%

\paragraph{Final OEP-based forms of the coupling constant.}
Gathering the results from Eqs. the coupling constant
can be given as follows
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep}
\Approx{ V_{in}^{A\rightarrow B} }{1}
       &= \sum_{\eta\in B}^{\rm RI} V^B_{n\eta} S_{\eta i} 
 +
2 S_{ni} u_i^{BA} \;, \\
%
\Approx{ V_{in}^{A\rightarrow B} }{2} &=
\Approx{ V_{in}^{A\rightarrow B} }{1} -
  \sum_{j   \in B}^{\rm Occ} S_{ij}
  \sum_{y   \in B}^{\rm At} q_y^{B,(nj)} w_{yi}^{BA}
\;,
\end{align}
\end{subequations}
%
where the auxiliary variables are
%
\begin{subequations}
\begin{align} \label{e:ct-murell-etal.vin.oep.aux-var}
 u_i^{BA} &\equiv    
 \sum_{y\in B}^{\rm At}
  \frac{Z_y}{ r_{yi} } 
 -
 \sum_{j\in B}^{\rm LC}
  \frac{2}{r_{ji}} 
                \;, \\
 w_{yi}^{BA} &\equiv 
   \sum_{x\in A}^{\rm At}
   \frac{Z_x}{r_{xy}}
  + \frac{1}{r_{iy}}
  - \sum_{k\in A}^{\rm Occ}
    \frac{2}{r_{ky}} 
                \;.
\end{align}
\end{subequations}
%
To compute the interaction energy due to CT from $A$ to $B$ by using the above SOA\hyp{}based
approximations, coupling elements need to be transformed from localized to canonical MO basis, i.e.,
%
\begin{equation} \label{e:ect-oep.prefinal}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{
 \lvert
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \Approx{V_{i'n}^{A\rightarrow B}}{} 
 \rvert^2 }{\varepsilon_i - \varepsilon_n} \;,
\end{equation}
%
where ${\bf L}^A$ is the CMO\hyp{}LMO transformation matrix for occupied orbitals of $A$. 
Note however, that the effective potential parameters from the density fitted term of group (i) 
do not involve any occupied orbitals.
Therefore, to save computational costs, only groups (ii) and (iii) need to be transformed
whereas for group (i) the overlap integrals from Eq.~\eqref{e:ct.group-i.final} 
can be already evaluated in CMO basis.
Thus, the final working formula for the interaction energy due to CT from $A$ to $B$ reads
%
\begin{multline} \label{e:ect-oep.final}
 E^{A\rightarrow B} \approx
 2 
 \sum_{i\in A}^{\rm CMO}
 \sum_{n\in B}^{\rm Vir}
 \frac{1}{\varepsilon_i - \varepsilon_n} \times 
 \Bigg(
   \Approx{V_{in}^{A\rightarrow B}}{\rm G1} \\
  +
   \sum_{i'\in A}^{\rm LMO} L_{ii'}^A
   \left\{
   \Approx{V_{i'n}^{A\rightarrow B}}{\rm G2} 
  +\Approx{V_{i'n}^{A\rightarrow B}}{\rm G3}
  \right\}
 \Bigg)^2 \;,
\end{multline}
%
where the subscripts G$n$ ($n$ = 1, 2, 3) denote a particular group of 
terms from Eqs.~\eqref{e:ct.group-i.final}, \eqref{e:ct.group-ii.final} and \eqref{e:ct.group-iii.final.a}
or \eqref{e:ct.group-iii.final.b}. 
The total CT energy is given by the sum of the above contribution and the twin contribution
due to CT from molecule $B$ to $A$.
